# Instrument creation

The pilot administrations consisted of 36 [items](https://docs.google.com/document/d/18KYE7jq8XLhN-mfGQRMnkf5AM-_U2CJck50eISbAiwM/edit?usp=sharing) that were presented in one of three administration groupings: 1) within substantive dimension, 2) within attitudinal dimension, and 3) random.

+ Demographic Information


## Content Validation

```{r contentvalidation, echo=FALSE, warning=FALSE, message=FALSE}

cvalid <- read.csv("Engagement Survey Content Validity.csv")

items <- nrow(cvalid)

```

7 Eagle I.O consultants were twice instructed to place each of `r items` items into one of three categories: Absorption, Dedication, or Vigor, and Cognitive, Affective, or Behavioral. Instructions asked each rater to:

> INSTRUCTIONS: Place an "X" in the column that you feel is the best fit for each item (only one "X" per row please)

The substantive scale definitions provided for ratings were: 

+ *Absorption*: Being fully immersed in one’s work, where time passes quickly and one has difficulty detaching from work tasks
+ *Vigor*: Experiencing persistent levels of energy, effort, and enthusiasm while working
+ *Dedication*: Experiencing pride and challenge in ones work, as well as strong feelings of support from and loyalty toward the organization

The attitudinal scale definitions were:

+ *Cognitive*: Pertaining to thoughts or general mental processes (for example what someone thinks)
+ *Affective*: Pertaining to feelings or emotions (for example, how someone feels)
+ *Behavioral*: Pertaining to acts or actions (for example, what someone does) 

The goal was to identify item(s) that were equally and heavily implicated with one substantive and one attitudinal scale.

Initial rating convergence for Absorption:

```{r absorption, echo=FALSE, warning=FALSE, message=FALSE}
## Absorption

table(cvalid[,c(6,2)])
table(cvalid[,c(6,3)])
table(cvalid[,c(6,4)])
```

Initial rating convergence for Vigor:

```{r vigor, echo=FALSE, warning=FALSE, message=FALSE}
## Vigor

table(cvalid[,c(7,2)])
table(cvalid[,c(7,3)])
table(cvalid[,c(7,4)])
```

Initial rating convergence for Dedication:

```{r dedication, echo=FALSE, warning=FALSE, message=FALSE}
## Dedication

table(cvalid[,c(8,2)])
table(cvalid[,c(8,3)])
table(cvalid[,c(8,4)])
```

