# Instrument creation

The pilot administrations consisted of 36 [items](https://docs.google.com/document/d/18KYE7jq8XLhN-mfGQRMnkf5AM-_U2CJck50eISbAiwM/edit?usp=sharing) that were presented in one of four administration groupings: 1) within substantive dimension (attitudinally grouped [but randomized within blocks of 4]), 2) within attitudinal dimension (substantively grouped [but randomized within blocks of 4]), 3) within substantive dimension (randomly distributed by attitude), and 4) within attitudinal dimension (randomly presented by substance).[^footie]

The four "experimental" conditions therefore prioritized and reflected the 3x3 groupings *or* one of the organization schemes (cognitive, affective, and behavioral *or* dedication, absorption, and vigor).
 
[^footie]: Decision was made on 10/13 to have the order of presentation *randomized* within each of the broader organization blocks (for example, Condition 3: all Affective, Cognitive, and Behavioral Absorption items were randomly administered, then all ABC Dedication items, etc [although DAC was also randomized by block such that not every respondent had the same DAC ordering])

We chose to control the order of item administration because of our *a priori* specification of a bi-factor structure, with the expectation that item ordering would serve as a response cue, yeilding stronger factor structural support based on the organization scheme. 

Our four item orderings were:

```{r cond1, echo=FALSE, warning=FALSE, message=FALSE}


cond1 <- read.csv("cond1.csv")
cond2 <- read.csv("cond2.csv")
cond3 <- read.csv("cond3.csv")
cond4 <- read.csv("cond4.csv")

library(kableExtra)


kable(cond1) 
kable(cond2) 
kable(cond3) 
kable(cond4) 

```


+ Demographic Information


## Content Validation

```{r contentvalidation, echo=FALSE, warning=FALSE, message=FALSE}

cvalid <- read.csv("Engagement Survey Content Validity.csv")

items <- nrow(cvalid)

```

7 Eagle I.O consultants were twice instructed to place each of `r items` items into one of three categories: Absorption, Dedication, or Vigor, and Cognitive, Affective, or Behavioral. Instructions asked each rater to:

> INSTRUCTIONS: Place an "X" in the column that you feel is the best fit for each item (only one "X" per row please)

## Administration condition

In order to randomize the administration of conditions, we asked respondents to indicate their birth month:

+ January $\rightarrow$ March: LINK ONE
+ April $\rightarrow$ June: LINK TWO
+ July $\rightarrow$ September: LINK THREE
+ October $\rightarrow$ December: LINK FOUR

The substantive scale definitions provided for ratings were: 

+ *Absorption*: Being fully immersed in one’s work, where time passes quickly and one has difficulty detaching from work tasks
+ *Vigor*: Experiencing persistent levels of energy, effort, and enthusiasm while working
+ *Dedication*: Experiencing pride and challenge in ones work, as well as strong feelings of support from and loyalty toward the organization

The attitudinal scale definitions were:

+ *Cognitive*: Pertaining to thoughts or general mental processes (for example what someone thinks)
+ *Affective*: Pertaining to feelings or emotions (for example, how someone feels)
+ *Behavioral*: Pertaining to acts or actions (for example, what someone does) 

The goal was to identify item(s) that were equally and heavily implicated with one substantive and one attitudinal scale.

Initial rating convergence for Absorption:

```{r absorption, echo=FALSE, warning=FALSE, message=FALSE}
## Absorption

table(cvalid[,c(6,2)])
table(cvalid[,c(6,3)])
table(cvalid[,c(6,4)])
```

Initial rating convergence for Vigor:

```{r vigor, echo=FALSE, warning=FALSE, message=FALSE}
## Vigor

table(cvalid[,c(7,2)])
table(cvalid[,c(7,3)])
table(cvalid[,c(7,4)])
```

Initial rating convergence for Dedication:

```{r dedication, echo=FALSE, warning=FALSE, message=FALSE}
## Dedication

table(cvalid[,c(8,2)])
table(cvalid[,c(8,3)])
table(cvalid[,c(8,4)])
```

