---
title             : "Development of an Intentional BiFactor Engagement Measure"
shorttitle        : "BiFactor Engagement"

author: 
  - name          : "Morgan Russell"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Casey Osorio-Duffoo"
    affiliation   : "2"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "1"
  - name          : "John Kulas"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Montclair State University"
  - id            : "2"
    institution   : "Harver"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Employee engagement has, in recent years, enjoyed a surge in popularity as a positive employee outcome.
  Despite this burgeoning interest, disagreement still remains regarding its factor structure and nomological relationship with similar concepts, such as burnout.
  

  
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "Engagement, engagement"
wordcount         : "X"

bibliography      : ["r-references.bib", "engage.bib", "siopadds.bib", "bifactor.bib", "book.bib", "renata.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

The roots of employee [aka work; e.g., @schaufeli_conceptualization_2010] engagement research likely started with theoretical expansions of forms of employee participation [see, for example, @ferris_added_1984] and job involvement [e.g., @elloy_examination_1991]. This exploration extended into broader considerations of attitudes and emotions [@staw_employee_1994] and were informed by further exploration of the dimensionality of constructs such as organizational commitment [@meyer_three-component_1991]. The 1990's saw focused development and refinement (for example, a dissertation; @leone_relation_1995 or actual semantic reference; @kahn_psychological_1990). @staw_employee_1994 investigated the relationships between *positive emotions* and favorable work outcomes, and although they do not use the word, "engagement", their distinction between felt and expressed emotion likely held influence upon the burgeoning interest in the engagement construct.

@kahn_psychological_1990 described engaged employees as being physically involved, cognitively vigilant, and emotionally connected. Although occasionally referred to as residing on the opposing pole to *burnout* [@maslach_early_2008], these two constructs are currently most commonly conceptualized as being distinct [@timms2012burnt; @kim_burnout_2009; @goering2017not; @schaufeli2008workaholism], although certainly not universally [@cole2012job; @taris2017burnout]. Comparing the two, @goering2017not concluded that they have a moderate (negative) association, but also distinct nomological networks. @schaufeli2008workaholism investigated both internal and external association indicators, concluding that engagement and burnout (as well as *workaholism*) should be considered three distinct constructs.

Burnout can be defined as a psychological syndrome characterized by exhaustion (low energy), cynicism (low involvement), and inefficacy (low self-efficacy), which is experienced in response to chronic job stressors [e.g., @leiter_areas_2004; @maslach1997causes]. Alternatively, engagement refers to an individual worker's involvement and satisfaction as well as enthusiasm for work [@harter_business-unit-level_2002]. @schaufeli_uwesutrecht_2003 further specify a "positive, fulfilling, work-related state of mind that is characterized by vigor, dedication, and absorption" (p. 74). Via their conceptualization, vigor is described as high levels of energy and mental resilience while working. Dedication refers to being strongly involved in one's work and experiencing a sense of significance, enthusiasm, inspiration, pride, and challenge. Absorption is characterized by being fully concentrated and happily engrossed in one's work, whereby time passes quickly and one has difficulties with detaching oneself from work [@schaufeli_measurement_2002]. This absorption element has been noted as being influenced in conceptual specification by [@csikszentmihalyi1990flow]'s concept of "flow".

Regarding measurement, Gallup is widely acknowledged as an early pioneer in the measurement of the construct [see, for example, @coffman_hard_1999]. The Utrecht Work Engagement Scale (UWES) is another self-report questionnaire developed by @schaufeli_uwesutrecht_2003 that directly assesses the vigor, dedication, and absorption elements.

> we need to do some market research on the Q12: 1. what's the feedback report look like? (google images show one overall "satsifaction" score and/or one overall "engagement" score), 2. how much does it cost, 3. what are the 200 pulse items Gallup refers to? (6/7/21)

Our conceptualization of work engagement is a mental state wherein employees...

-   ...feel energized (**Vigor**)
-   ...are enthusiastic about the content of their work and the things they do (**Dedication**)
-   ...are so immersed in their work activities that time seems compressed (**Absorption**)

# Methods

## Participants

```{r getData, echo=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
#CFA Analysis

temp <- read.csv("qualtrics_pilot_data.csv", header=FALSE, na.strings="")

x <- temp[2,]
data <- temp[-c(1:3),]
colnames(data) <- x

num <- nrow(data)

temp$V163 <- temp$V163 %>% 
  gsub("[^0-9./-]", "", .) %>%  # removes all characters not included in brackets
  gsub(".*/", "", .) %>% # Selects second number after "/" (e.g. 40/50 -> 50)
  gsub(".*-", "", .) %>%  # Selects second number after "-" (e.g. 50-60 -> 60)
  gsub("[^0-9]", "", .) %>% # Removes
  str_sub(1,2) %>% # Subsets all responses to first two indices. Quick and easy way to rule out impossible hour entries
  as.numeric()

demo_table <- datatable(temp[7:333,162:164], colnames = c("What is the title of the job you were thinking about while responding to this survey?", "How many hours do you typically work per week in this job?", "How long have you been with this organization?"))
```

`r num` individuals provided ratings across 36 candidate items. These participants were gathered via snowball sampling.

Participant job title, hours worked per week, and organizational tenure were recorded. Mean hours worked per week was `r mean(temp$V163, na.rm = TRUE)`

Mean organizational tenure was INSERT HERE, with a standard deviation of INSERT HERE. YOU NEED TO RECODE TENURE TO ACCOUNT FOR MONTHS/YEARS. Participants who did not exactly specify their tenure (e.g. "A bit over a year") were not included in this average.

`r demo_table`

## Material

## Procedure

Looking into the specification of polychoric covariances [@joreskog1994estimation]. This seems to be not very commonly leveraged (only package that seems to estimate these is `semPlot`). We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. We took two different approaches to determining final scale definitions: 1) focus on corrected item-total correlations, and 2) focus on CFA modificiation indices.

### CFA Modification Indices

Looking at the substantive and attitudinal models independently, we requested modification indices from each, with the intent of retaining indicators whose shared residual covariances were implicated as being "freed". The path with the highest modification index across both CFA's was between item2 and item4, which are both indicators of "Absorption" and "Cognition". One of these items was therefore a candidate for deletion, and semantic preference was given to item4, "I find it difficult to mentally disconnect from work" over item2, "I have a hard time detaching mentally from my work". After item2 was excluded from both scale definitions (substantive and attitudinal), the CFAs were re-run and modification indices re-checked for bi-factor structure optimizing modifications.[^1]

[^1]: Probably put a table in here highlighting certain modification indices (with a key to intended factor-item association).

We prioritized item deletions such that an item was implicated for deletion if: 1) modification index was high (relative to others) and 2) error residual was within same "cell". The choice of itme to delete was based on author preference for wording/semantics as well as construct element coverage (considering the possible consequences for construct deficiency). Item variance was also consulted (retention more likely with greater item variance).

> > Actually it doesn't matter that much with only 1 item deletion - probably go ahead and do a few before recheck modification indices

### Single factor versus bifactor approaches

## Data analysis

We used `r cite_r("r-references.bib")` for all our analyses.

# Results

CFA drafts below

```{r CFA.sub, echo=FALSE, warning=FALSE, fig.cap="Substantive factor structure CFA"}

## getting conditions into one large file below - 12/9/20

data$Cond1 <- rowSums(is.na(data[18:53]))
data$Cond2 <- rowSums(is.na(data[54:89]))
data$Cond3 <- rowSums(is.na(data[90:125]))
data$Cond4 <- rowSums(is.na(data[126:161]))

data$Condition[data$Cond1 < 36] <- 1
data$Condition[data$Cond2 < 36] <- 2
data$Condition[data$Cond3 < 36] <- 3
data$Condition[data$Cond4 < 36] <- 4

cond1 <- data[ which(data$Condition==1), ]
cond2 <- data[ which(data$Condition==2), ]
cond3 <- data[ which(data$Condition==3), ]
cond4 <- data[ which(data$Condition==4), ]

cond1.red <- cond1[,c(6, 18:53, 162:165, 171)]  ## using Cond1 ordering
cond2.red <- cond2[,c(6, 62:65, 70:73, 82:85, 58:61, 74:77, 86:89, 66:69, 78:81, 54:57, 162:165, 171)]
cond3.red <- cond3[,c(6, 94:97, 106:109, 118:121, 98:101, 110:113, 122:125, 102:105, 114:117, 90:93, 162:165, 171)]
cond4.red <- cond4[,c(6, 138:161, 130:137, 126:129, 162:165, 171)]        ## 171 versus 172 because testing script has extra "hours" variable

names(cond1.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond1.red))      ## Getting rid of condition markers so rbind will work
names(cond2.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond2.red))  
names(cond3.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond3.red))  
names(cond4.red) = gsub(pattern = "C*.* - ", replacement = "", x = names(cond4.red))  

together <- rbind(cond1.red, cond2.red, cond3.red, cond4.red)        ## we'll be using this object for analyses

num_valid <- nrow(together)

i <- c(1:37)                                          ## Changing item responses to numerics
together[ , i] <- apply(together[ , i], 2,            # Specify own function within apply
                        function(x) as.numeric(as.character(x)))


##########################################################
##########################################################
##########################################################
############# RECODES

together$`Most days, I feel happiest when the workday is soon to be complete.` <- 7 - together$`Most days, I feel happiest when the workday is soon to be complete.`
together$`This job drains my energy.` <- 7 - together$`This job drains my energy.`

## BEHAVIORAL (NONE):

## COGNITIVE: 

together$`Thinking about work saps my energy.` <- 7 - together$`Thinking about work saps my energy.`
together$`I often think about finding another job.` <- 7 - together$`I often think about finding another job.`


library(lavaan)
library(sem)
library(semPlot)
library(dplyr)
 

CFAdata<-together[,2:37]


CFAdata<-CFAdata%>%rename(
  Item_1=`I’m able to concentrate on my work without distractions.`,
  Item_2=`I have a hard time detaching mentally from my work.`,
  Item_3=`Time passes quickly while I’m working.`,
  Item_4=`I find it difficult to mentally disconnect from work.`,
  Item_5=`I enjoy thinking about work even when I’m not at work.`,
  Item_6=`Most days, I feel happiest when the workday is soon to be complete.`,
  Item_7=`I am happiest when I am immersed in a project.`,
  Item_8=`I love starting my workday.`,
  Item_9=`I devote more time than is expected of me.`,
  Item_10=`I have to be reminded to take breaks while I’m at work.`,
  Item_11=`I never miss a work deadline.`,
  Item_12=`I never allow distractions to interfere with my work.`,
  Item_13=`I devote my full attention to my work tasks throughout the day.`,
  Item_14=`Thinking about work saps my energy.`,
  Item_15=`I would rather direct my focus toward a work task than a personal task.`,
  Item_16=`I’m able to maintain good levels of energy throughout the workday.`,
  Item_17=`I enjoy spending time completing my job tasks.`,
  Item_18=`Most days I feel enthusiastic about starting my work day.`,
  Item_19=`I feel motivated to go beyond what is asked of me.`,
  Item_20=`This job drains my energy.`,
  Item_21=`When work is slow I find ways to be productive.`,
  Item_22=`I express enthusiasm for my job while at work.`,
  Item_23=`I try my best to perform well at work.`,
  Item_24=`If I notice my energy level is low, I take corrective steps to re-energize.`,
  Item_25=`I plan my future with this company.`,
  Item_26=`I believe this company cares about my career goals.`,
  Item_27=`I often think about finding another job.`,
  Item_28=`This organization challenges me to work at my full potential.`,
  Item_29=`I am proud to be a member of this organization.`,
  Item_30=`I feel supported by my supervisor when I fail at a task.`,
  Item_31=`I feel proud of my accomplishments within this organization.`,
  Item_32=`My job makes me feel like I’m part of something meaningful.`,
  Item_33=`I make valued contributions to the organization.`,
  Item_34=`I embrace challenging situations at work.`,
  Item_35=`I speak positively about this organization to others.`,
  Item_36=`This organization provides the resources necessary for me to successfully perform my job.`
)


Sub_Model<-'
Absorption=~Item_1+Item_2+Item_3+Item_4+Item_5+Item_6+Item_7+Item_8+Item_9+Item_10+Item_11+Item_12
Vigor=~Item_13+Item_14+Item_15+Item_16+Item_17+Item_18+Item_19+Item_20+Item_21+Item_22+Item_23+Item_24
Dedication=~Item_25+Item_26+Item_27+Item_28+Item_29+Item_30+Item_31+Item_32+Item_33+Item_34+Item_35+Item_36
'

Fit1.1<-lavaan::cfa(Sub_Model, data = CFAdata)
semPlot::semPaths(Fit1.1, "std")
fit1.1 <- as.data.frame(fitMeasures(Fit1.1))
# summary(Fit1.1, fit.measure=TRUE)

# write.csv(modindices(Fit1.1, sort=TRUE), "fit_substantive.csv")

```

```{r CFA.att, echo=FALSE, warning=FALSE, fig.cap="Attitudinal factor structure CFA"}


Att_Model<-'
Cognitive=~Item_1+Item_2+Item_3+Item_4+Item_13+Item_14+Item_15+Item_16+Item_25+Item_26+Item_27+Item_28
Affective=~Item_5+Item_6+Item_7+Item_8+Item_17+Item_18+Item_19+Item_20+Item_29+Item_30+Item_31+Item_32
Behavioral=~Item_9+Item_10+Item_11+Item_12+Item_21+Item_22+Item_23+Item_24+Item_33+Item_34+Item_35+Item_36
'
Fit1.2<-lavaan::cfa(Att_Model, data = CFAdata)
semPlot::semPaths(Fit1.2,"std")
# lavaan::fitMeasures(Fit1.2)
# summary(Fit1.2, fit.measure=TRUE)

```

# Discussion

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

\endgroup
